### 2021-09-07 input/conclusion.tex
cheating on biblio + changes here and there to get to 16 pages

As future work, we plan on extending the logical partitioning protocol
to enable lazy retrieval of partitions. Indeed, using \NAME, every
\process partakes in the propagation of indexes of content and
replicas. We would like to leverage the hierarchical properties of
interconnected autonomous systems to limit the propagation of such
indexes only to interested systems.
%
%% As ongoing and future work, we are currently studying how it might be
%% possible to limit the scope of a partition to one autonomous system at
%% most. Indeed, the gain of propagating changes to \processes belonging to
%% another autonomous system might be negligible as the latency penalty
%% is mainly due to inter autonomous systems' links (\eg trans-continental
%% links).  Exactly, we are investigating how such a change can be
%% formalized and its impact on the current protocol.
%
%autonomous systems. Indeed, \processes could leverage the hierarchical
%properties of the Internet topology~\cite{nur2018geography} to avoid
%flooding the whole systems with control information about all
%partitions.
%\TODO{should we highlight this at the end of the experiment}
%

>>>>

As future work, we plan to enable lazy retrieval of partitions when a
large number of \TODO{objects} is involved. Indeed, using \NAME, every
\process partakes in the propagation of all indexes which raises
scalability issues. We would like to leverage the hierarchical
properties of
% interconnected
autonomous systems to limit the
propagation of such indexes only to interested systems.

%
%% As ongoing and future work, we are currently studying how it might be
%% possible to limit the scope of a partition to one autonomous system at
%% most. Indeed, the gain of propagating changes to \processes belonging to
%% another autonomous system might be negligible as the latency penalty
%% is mainly due to inter autonomous systems' links (\eg trans-continental
%% links).  Exactly, we are investigating how such a change can be
%% formalized and its impact on the current protocol.
%
%autonomous systems. Indeed, \processes could leverage the hierarchical
%properties of the Internet topology~\cite{nur2018geography} to avoid
%flooding the whole systems with control information about all
%partitions.
%\TODO{should we highlight this at the end of the experiment}
%
